
	
\section{Project Requirements}
	\subsection{Constraints}
	There are two constraints imposed on this project.
	\subsubsection{Deliverables}
	The project has the following deliverables that are required for success:
	\begin{itemize}
		\item This Report
		\item The Program
		\item The Poster
	\end{itemize}
	\subsubsection{Time Constraint}
	This project is to be finished by April 22nd, 2021\footnote{Needs to be verified}.
	
	\subsection{Functional Requirements}
	The functional requirements of the project include minimum requirements and those which we would like to implement, the latter will be diliminated by a star *:
	\subsubsection{Primary Requirements}
	The primary requirements are those which are to always be functional:
	\begin{itemize}
		\item Ability for the user to play a game:
		\begin{itemize}
			\item Against another user locally.
			\item Against an \emph{AI} that will be provided.*
		\end{itemize}
	\item Ability for the user to track their \emph{statistics} of play over the lifetime of their account including wins, losses, and draws.\footnote{This does not include syncing which is a secondary requirement.}
	\item Ability for the user to modify the starting layout of the chess pieces to match a configuration of either a previously ongoing game or a game scenario. 
	\begin{itemize}
		\item FEN Processing
		\item FEN Interpretation
		\item FEN Generation
	\end{itemize}
	\end{itemize}
	\subsubsection{Secondary Requirements}
	Secondary requirements are those which will not always be available.
	\begin{itemize}
		\item Ability for the user to create an account to access online features.
		\begin{itemize}
			\item Ability for the user to sync statistics.
			\item Ability for the user to play against another user online.
		\end{itemize}
	\item Ability for the user to login via their Google Account credentials.
	\end{itemize}
	\subsection{Usability}
	\subsubsection{User Interface}
	
	\subsubsection{Performance}
	
	\subsection{System}
	\paragraph{Serverside}
	All server-side requirements of the this project were provided by eco.webhosting.co.uk
	
	The requirements of the server include:
	\begin{itemize}
		\item Web Server setup to run Angular applications
		\item Database running MySQL 10.4.14
		\item Can handle multiple requests and sessions at a given time.
	\end{itemize}

	\paragraph{Clientside}
	The client side requirements are recommended requirements based on our own systems:
	\subparagraph{Operating System}
	This program does not require a specific Operating System.
	\subparagraph{Memory}
	The system should have at least 2GB of RAM.
	\subparagraph{Required Software}
	This program requires a modern GUI web browser, preferably:
	\begin{itemize}
		\item Firefox 
		\item Google Chrome
		\item Brave
	\end{itemize}
	\subsection{Database}
	This project will be using one database to keep track of ongoing games which is using MySQL version 10.4.14.
	\subsection{Networking}
	All project artifacts and interconnectivities are being provided by the hosing web server.
	\subsection{Security}
	For Google Authentication, we will be leveraging Google OAuth 2.0 API. The other security requirements are inherently provided by the hosting server.

