\section{Project Specification}
\subsection{Focus}
The focus of this project is to gain experience with Angular and Node.js\footnote{Devin didn't know about Angular until this project, and only used NPM to download software.}. Where applicable this project will attempt to utilize open-source projects and existing systems when achievable. 
\paragraph{FEN} We are using FEN (Forsyth Edwards Notation) to keep track of the positions and moves on the board. This is supported by similar applications and programs that could enhance the application such as Stockfish (w/ UCI) if implemented.
\subsection{Platform}
This project is developing a web application. The application will be \emph{portable} to devices that have an acceptable screen size.
\subsection{Genre}
This project is developing a MMO*\footnote{Optional Requirement} board game.
\subsection{Target Audience}
The target audience for this project is for competitive chess players to test moves. This means that the program will need to implement all the chess rules properly and that the systems for processing and interpreting chess moves of import.
\subsection{Development Environment}
\paragraph{Devin} Uses vim(neovim), emacs, Bluefish, angular cli, and Firefox Developer tools.
\subsubsection{Libraries}
The project utilizes Angular Framework and Google Identity API (User Authentication), both have their own dependencies which are imported.
\subsubsection{Frameworks}
This project is developed using the Angular Framework (11.1.2) with TypeScript (and CSS) along with Bootstrap CSS Framework.

