% Created 2021-02-17 Wed 16:38
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Devin Michael O'Brien}
\date{\today}
\title{Chess Editor}
\hypersetup{
 pdfauthor={Devin Michael O'Brien},
 pdftitle={Chess Editor},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

\maketitle
\tableofcontents

\section{Project Definition}
\label{sec:orgb20949e}
People like Chess and need a way to quickly develop and practice new strategies. I love
Chess!!! Chess Editor will let people play Chess on their PC and set up the board the
way they want to test different strategies, or just play in a different way. It will support
playing against an AI, or playing against another person locally. It will include an account
system to track wins and losses. For the purposes of testing, there will be an undo and
redo button, as well as tools to set up specific board scenarios. It will be programmed in
Typescript and we will use Stockfish for the AI.
\section{{\bfseries\sffamily TODO} Project Requirements [1/4]}
\label{sec:orgfb85e42}
\subsection{{\bfseries\sffamily DONE} Functional [2/2]}
\label{sec:orgdbf309f}
\subsubsection{{\bfseries\sffamily DONE} Primary Requirements}
\label{sec:org54f4998}
The primary soce of functionality for \emph{/ \textbf{Chess Editor} /} include:
\begin{itemize}
\item Ability for the user to play an online game of chess with
another user, or alternatively against \textbf{AI} that will be
provided,
\item Ability for the user to track their \textbf{statistics} of play over
the life of their account; such as:
\begin{itemize}
\item Wins
\item Losses
\item Draws
\end{itemize}
\item Ability for the user to modify the starting layout of the chess
pieces to match the configuration of either a previously ongoing
game or a chess scenario.
\end{itemize}
\subsubsection{{\bfseries\sffamily DONE} Secondary Requirements}
\label{sec:org1390d35}
The secondary scope of functionality for Chess Editor include:
\begin{itemize}
\item Ability for the end user to create an account to access features
\item Ability for the end user to login via their Google Account credentials.
\end{itemize}
\subsubsection{Optional Requirements}
\label{sec:orgb9af487}
\subsection{{\bfseries\sffamily TODO} Usability [0/2]}
\label{sec:orge2ec26e}
\subsubsection{{\bfseries\sffamily TODO} User Interface}
\label{sec:orgdbd0401}
The user interface of the application must not be obtrusive and
needs to be adapted for mobile devices.
\subsubsection{{\bfseries\sffamily TODO} Performance}
\label{sec:org15e218a}
The performance of the application must not interfere with other
processes on the users system.
\subsection{{\bfseries\sffamily TODO} System [0/3]}
\label{sec:org2675774}
\subsubsection{{\bfseries\sffamily TODO} Hardware}
\label{sec:org27dec61}
The application will require hardware capable of running a modern web-brower without difficulty.
Please add table of estimate
\subsubsection{{\bfseries\sffamily TODO} Software}
\label{sec:orge0244f9}
The application will require a modern web-browser preferably one of the following:
Add a table of web-browsers
\subsubsection{{\bfseries\sffamily TODO} Database\hfill{}\textsc{Verify}}
\label{sec:orgcbf4328}
This project will have one database which is used to keep track of on-going games.
\subsection{{\bfseries\sffamily TODO} Security}
\label{sec:org82ea64f}

\section{Project Specification}
\label{sec:orgaa08407}
\subsection{Focus}
\label{sec:org00e3bce}
This project has a focus on developing experience with Angular and
with a client-server application. This project will attempt to utilize
open-source projects when it is reasonably possible.

\subsection{Development Environemnt}
\label{sec:org558edd4}
\subsubsection{Libraries}
\label{sec:orga693088}
This project will be using the Google Identity API for user Authentication.
\subsubsection{Frameworks}
\label{sec:org67f148d}
This project will be developed using the Angular framework (11.1.2)
with TypeScript.
\subsection{Platform}
\label{sec:org3feb2ce}
This project is going to be web-based application,
\subsection{Genre}
\label{sec:orge2a5561}
This project is considered as an online board game.
\section{System Design}
\label{sec:org8c257f6}
\subsection{Subsystem Identification}
\label{sec:org9f8e945}
\subsubsection{Sequence Diagram\hfill{}\textsc{@DeMO}}
\label{sec:org474874a}
I have previously made the sequence diagram, but I have had to redo it a couple times
as we have continued, the design has changed. I am going to just upload an complete 
sequence diagram and since it doesn't have to be the same and can be used in refinement
section.
\subsubsection{Use-Case Diagram}
\label{sec:org0dc7b17}

\subsubsection{Class Diagram\hfill{}\textsc{@Dakota:@Tyler:@DeMO:@pawilliamson}}
\label{sec:org779b03e}

\subsubsection{State Diagram}
\label{sec:org916ef68}
\subsection{Design}
\label{sec:org5080350}
\subsubsection{Mock-up Diagram}
\label{sec:orgc8e6978}
\subsubsection{Color Schemes}
\label{sec:orgd4f23f7}
\subsubsection{{\bfseries\sffamily TODO} Additional Comments}
\label{sec:orgd1a30d5}
We will be using Bootstrap framewwork.
\subsection{Sub-System Communication}
\label{sec:org3d5c8d8}
\subsubsection{Controls}
\label{sec:orge9a7ffc}
\subsubsection{I/O}
\label{sec:orga0d9841}
\subsubsection{Dataflow\hfill{}\textsc{@Tyler}}
\label{sec:org31f7bd8}
\subsection{{\bfseries\sffamily TODO} Entity Relationship Model (E-R Model)}
\label{sec:org45ed458}
\subsection{{\bfseries\sffamily TODO} Overall operation - System Model}
\label{sec:org49d2edd}
\section{{\bfseries\sffamily TODO} System Analysis}
\label{sec:org76bfca0}

\section{{\bfseries\sffamily TODO} Project Scrum Report}
\label{sec:org7495096}
\subsection{Overall}
\label{sec:orgaf86fa2}
\subsection{Product Backlog}
\label{sec:orge7aaca8}
\subsection{Sprint Backlog}
\label{sec:org73af022}
\subsection{Burndown Chart}
\label{sec:orgd97450a}
\subsection{Sprint 1}
\label{sec:org208e456}
Sprint 1 began on January 22, 2021 and continued to Febuary
6, 2021. The period lasted one day longer than the allocated duration.
\subsubsection{Scrum}
\label{sec:orgdc794fa}
During sprint, two scrum meetings took place
\begin{itemize}
\item January 28, 2021: Discussed the framework of the project and
decided to use Angular. Discussed the scope of the project and
decided to be a web application. Discussed authentication
services for the server.
\item February 4, 2021: Discussed some work that was done since the
previous scrum; includes diagrams and investigations of Google
Authentication viability for the server.

\begin{center}
\begin{tabular}{llll}
Item & Created BY & Date & Status\\
Project Definition & dobrienUNCG & 01/21/21 & Completed by pizzaza\\
Project requirements & dobrienUNCG & 01/21/21 & Completed during Scrums 1 and 2 by group\\
Identify subsystems & dobrienUNCG & 01/21/21 & Moved to Sprint 2 backlog\\
Project Specification & dobrienUNCG & 01/21/21 & Moved to sprint 2 backlog\\
\end{tabular}
\end{center}
\end{itemize}

\section{{\bfseries\sffamily TODO} Subsystems [/]}
\label{sec:org03c7b0f}
\subsection{{\bfseries\sffamily TODO} Chess Game [0/7]\hfill{}\textsc{@Tyler:@Dakota}}
\label{sec:orgdc962f0}
\subsubsection{{\bfseries\sffamily TODO} Initial Design and Model}
\label{sec:org33da27e}
\subsubsection{{\bfseries\sffamily TODO} Data Dictionary}
\label{sec:org260d33a}
\subsubsection{{\bfseries\sffamily TODO} Revisions (Refinement)}
\label{sec:org22b4fb6}
\subsubsection{{\bfseries\sffamily TODO} Scrum Backlog}
\label{sec:org65cf748}
\begin{center}
\begin{tabular}{llll}
Task & On & Assigned To & Completed On\\
--------------------------- & -- & ------------ & -----------\\
Generate Chessboard &  & Tyler, Dakota & \\
Chess Pieces &  &  & \\
Movement &  &  & \\
Movement and player interfaces &  &  & \\
Display Board &  &  & \\
Drag and move piece` &  &  & \\
Validate Moves &  &  & \\
Detect Check &  &  & \\
Detect Win &  &  & \\
\end{tabular}
\end{center}
\begin{enumerate}
\item {\bfseries\sffamily TODO} User Story Categories\hfill{}\textsc{@DeMO}
\label{sec:org0feb27f}
\end{enumerate}
\subsubsection{{\bfseries\sffamily TODO} Coding}
\label{sec:org667dba5}
\begin{enumerate}
\item Language
\label{sec:org3ab076c}
\end{enumerate}
\subsubsection{{\bfseries\sffamily TODO} User Training}
\label{sec:orgb2f6dbb}
\subsubsection{{\bfseries\sffamily TODO} Testing}
\label{sec:org2f6d543}
\subsection{{\bfseries\sffamily TODO} User Authentication [0/7]\hfill{}\textsc{@pawilliamson}}
\label{sec:org73ca7b6}
\subsubsection{{\bfseries\sffamily TODO} Initial Design and Model}
\label{sec:orgb8760eb}
\subsubsection{{\bfseries\sffamily TODO} Data Model}
\label{sec:org5ced554}
\subsubsection{{\bfseries\sffamily TODO} Refinement}
\label{sec:orgb80ab0c}
\subsubsection{{\bfseries\sffamily TODO} Scrum Backlog}
\label{sec:org6f1c72d}
\begin{enumerate}
\item {\bfseries\sffamily TODO} User Story Categories\hfill{}\textsc{@DeMO}
\label{sec:org8e60305}
\end{enumerate}
\subsubsection{{\bfseries\sffamily TODO} Coding}
\label{sec:org2996c9b}
\subsubsection{{\bfseries\sffamily TODO} User Training}
\label{sec:org8edbb2d}
\subsubsection{{\bfseries\sffamily TODO} Testing}
\label{sec:org65c28ba}
\subsection{{\bfseries\sffamily TODO} Server - Client [0/7]\hfill{}\textsc{@Tyler}}
\label{sec:org0647564}
\subsubsection{{\bfseries\sffamily TODO} Initial Design and Model}
\label{sec:orgadeeb28}
\subsubsection{{\bfseries\sffamily TODO} Data Dictionary}
\label{sec:orga3771cc}
\subsubsection{{\bfseries\sffamily TODO} Refinement}
\label{sec:org8df178e}
\subsubsection{{\bfseries\sffamily TODO} Scrum Backlog}
\label{sec:org3a7233a}
\subsubsection{{\bfseries\sffamily TODO} Coding}
\label{sec:org99c3f3d}
\subsubsection{{\bfseries\sffamily TODO} User Training}
\label{sec:org9496414}
\subsubsection{{\bfseries\sffamily TODO} Testing}
\label{sec:org230d570}
\subsection{{\bfseries\sffamily TODO} Computer Opponent  [0/7]\hfill{}\textsc{@DeMO}}
\label{sec:orgf838c81}
\subsubsection{{\bfseries\sffamily TODO} Initial Design and Model}
\label{sec:org6ece6c8}
\subsubsection{{\bfseries\sffamily TODO} Data Dictionary}
\label{sec:orgf9866c3}
\subsubsection{{\bfseries\sffamily TODO} Refinement}
\label{sec:orgb2dc701}
\subsubsection{{\bfseries\sffamily TODO} Scrum Backlog}
\label{sec:org0068398}
\begin{enumerate}
\item {\bfseries\sffamily TODO} User Story Categories
\label{sec:org5c18c55}
\end{enumerate}
\subsubsection{{\bfseries\sffamily TODO} Coding}
\label{sec:org8a6197d}
\subsubsection{{\bfseries\sffamily TODO} User Training}
\label{sec:orge31abcc}
\subsubsection{{\bfseries\sffamily TODO} Testing}
\label{sec:org4d86b18}
\section{{\bfseries\sffamily TODO} Complete System}
\label{sec:org64ebb9a}
\subsection{{\bfseries\sffamily TODO} Final Product}
\label{sec:org6d46a23}
\subsection{{\bfseries\sffamily TODO} Source code and user manual + Technical Report}
\label{sec:org54beef9}
\subsubsection{{\bfseries\sffamily TODO} GitHub}
\label{sec:org6f68d1f}
\subsection{{\bfseries\sffamily TODO} Evaluation by client and instructor}
\label{sec:org8bc8658}

\subsection{{\bfseries\sffamily TODO} Team Member Description}
\label{sec:org350429c}
Our team consists of five members: Dakota Simpkins, Tyler Wallshleger,
Devin O'Brien, Preston Williamson, and Brandon Kyle.
\subsubsection{Dakota Simpkins}
\label{sec:org22e14b5}
\subsubsection{Tyler Wallshleger}
\label{sec:org55d4c8c}
\subsubsection{Devin O'Brien}
\label{sec:orgff4f13c}
\subsubsection{Preston Williamson}
\label{sec:org6fdd71f}
\subsubsection{Brandon Kyle}
\label{sec:org29679ea}
\end{document}
